### 2020-08-13 code/figure2.Rmd

```{r figure-2-plot, fig.align= 'center', fig.height= 7, fig.width = 7}
#out.height='90%', out.width='90%'
## top100 pathways pancancer oncoprint
load("../data/onco_ggplot.Rda") ## load data
onco_color <- c("0" = "grey", "1" = "firebrick3") ## color scheme for oncoprint

>>>>

```{r figure-5-plot, fig.align= 'center', fig.height= 7, fig.width = 7}
#out.height='90%', out.width='90%'
## top100 pathways pancancer oncoprint
load("../data/onco_ggplot.Rda") ## load data
onco_color <- c("0" = "grey", "1" = "firebrick3") ## color scheme for oncoprint
